---
title: "Business Intelligence Lab Submission Markdown"
author: "Team Marafiki"
date: "17/10/2023"
output:
  github_document:
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
editor_options:
  chunk_output_type: console
---

# Student Details

+---------------------------------------------------+---------------------------------------------+
| **Student ID Numbers and Names of Group Members** | 1.  136446 - C - Mirav Bhojani              |
|                                                   |                                             |
|                                                   | 2.  136788 - C - Derrick Nyaga              |
|                                                   |                                             |
|                                                   | 3.  136709 - C - Jane Mugo                  |
|                                                   |                                             |
|                                                   | 4.  136895 - C - Wesley Wanyama             |
|                                                   |                                             |
|                                                   | 5.  135399 - C - Sheilla Kavinya            |
+---------------------------------------------------+---------------------------------------------+
| **GitHub Classroom Group Name**                   | *Team Marafiki*                             |
+---------------------------------------------------+---------------------------------------------+
| **Course Code**                                   | BBT4206                                     |
+---------------------------------------------------+---------------------------------------------+
| **Course Name**                                   | Business Intelligence II                    |
+---------------------------------------------------+---------------------------------------------+
| **Program**                                       | Bachelor of Business Information Technology |
+---------------------------------------------------+---------------------------------------------+
| **Semester Duration**                             | 21^st^ August 2023 to 28^th^ November 2023  |
+---------------------------------------------------+---------------------------------------------+
# Setup Chunk


We start by installing all the required packages

```{r Install Packages, echo=TRUE, message=FALSE, warning=FALSE}
if (require("ggplot2")) {
  require("ggplot2")
} else {
  install.packages("ggplot2", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## caret ----
if (require("caret")) {
  require("caret")
} else {
  install.packages("caret", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## mlbench ----
if (require("mlbench")) {
  require("mlbench")
} else {
  install.packages("mlbench", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## pROC ----
if (require("pROC")) {
  require("pROC")
} else {
  install.packages("pROC", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## dplyr ----
if (require("dplyr")) {
  require("dplyr")
} else {
  install.packages("dplyr", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

if (!require("readr")) {
  install.packages("readr", dependencies = TRUE, 
                   repos = "https://cloud.r-project.org")
}
```


**Note:** the following "*KnitR*" options have been set as the defaults in this markdown:\
`knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE, collapse = FALSE, tidy.opts = list(width.cutoff = 80), tidy = TRUE)`.

More KnitR options are documented here <https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html> and here <https://yihui.org/knitr/options/>.

```{r setup, echo=TRUE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
	eval = TRUE,
	echo = TRUE,
	warning = FALSE,
	collapse = FALSE,
	tidy = TRUE
)
```

------------------------------------------------------------------------

**Note:** the following "*R Markdown*" options have been set as the defaults in this markdown:

> output:\
> \
> github_document:\
> toc: yes\
> toc_depth: 4\
> fig_width: 6\
> fig_height: 4\
> df_print: default\
> \
> editor_options:\
> chunk_output_type: console


# Load the BreastCancer dataset


```{r Load dataset}
data("BreastCancer")
```


# Determine the Baseline Accuracy 
```{r Baseline Accuracy}
breast_cancer_freq <- BreastCancer$Class
result <- cbind(frequency = table(breast_cancer_freq), percentage = prop.table(table(breast_cancer_freq)) * 100)

# Print the frequency and percentage table
print(result)
````


